\LaTeX\ Author Guidelines for 3DV Proceedings

### 2016-06-21 3dv2016authorkit/latex/egpaper_final.tex
added 3dv 2016 template

By submitting a manuscript to 3DV, the authors assert that it has not been
previously published in substantially similar form. Furthermore, no paper
which contains significant overlap with the contributions of this paper
either has been or will be submitted during the 3DV 2015 review period to
{\bf either a journal} or any conference or any
workshop.
 {\bf Papers violating this condition will be rejected.}

@@

\subsection{Paper length}
3DV papers should be no longer than 8 pages, excluding references, and no longer than 
9 pages in total length. Overlength papers will simply not be reviewed.  This includes papers
where the margins and formatting are deemed to have been significantly
altered from those laid down by this style guide.  Note that this
\LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for
supervised revisions of manuscripts.  The reviewing process cannot determine
the suitability of the paper for presentation in eight pages if it is
reviewed in eleven.

>>>>

By submitting a manuscript to 3DV, the authors assert that it has not been
previously published in substantially similar form. Furthermore, no paper
which contains significant overlap with the contributions of this paper
either has been or will be submitted during the 3DV 2016 review period to
{\bf either a journal} or any conference or any
workshop.
 {\bf Papers violating this condition will be rejected.}

@@

\subsection{Paper length}
3DV papers should be no longer than 8 pages, excluding references.
The references section will not be included in the page count, and
there is no limit on the length of the references section. Overlength
papers will simply not be reviewed.  This includes papers where the
margins and formatting are deemed to have been significantly altered
from those laid down by this style guide.  Note that this \LaTeX\ 
guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no
provision for supervised revisions of manuscripts.  The reviewing
process cannot determine the suitability of the paper for presentation
in eight pages if it is reviewed in eleven.

### 2016-06-21 3dv2016authorkit/latex/egpaper_for_review.tex
added 3dv 2016 template

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
%\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

\threedvfinalcopy % *** Uncomment this line for the final submission

@@

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifthreedvfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

@@

\maketitle
%\thispagestyle{empty}

@@

By submitting a manuscript to 3DV, the authors assert that it has not been
previously published in substantially similar form. Furthermore, no paper
which contains significant overlap with the contributions of this paper
either has been or will be submitted during the 3DV 2016 review period to
{\bf either a journal} or any conference or any
workshop.
 {\bf Papers violating this condition will be rejected.}

@@

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.  Just
because you didn't refer to it in the text doesn't mean some future reader
might not need to refer to it.  It is cumbersome to have to use
circumlocutions like ``the equation second from the top of page 3 column
1''.  (Note that the ruler will not be present in the final copy, so is not
an alternative to equation numbers).  All authors will benefit from reading
Mermin's description of how to write mathematics.%: \url{http://www.pamitc.org/documents/mermin.pdf}.

@@

FAQ: Are acknowledgments OK?  No.  Leave them for the final copy.

@@

All printed material, including text, illustrations, and charts, must be kept
within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
high.  Page numbers should be in footer with page numbers, centered and .75
inches from the bottom of the page and make it start at the correct page
number rather than the 4321 in the example.  To do this find the line (around
line 23)  
\begin{verbatim}
%\ifthreedvfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\end{verbatim}
where the number 4321 is your assigned starting page.

Make sure the first page is numbered by commenting out the first page being
empty on line 47
\begin{verbatim}
%\thispagestyle{empty}
\end{verbatim}

>>>>

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%\threedvfinalcopy % *** Uncomment this line for the final submission

@@

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifthreedvfinal\pagestyle{empty}\fi
\begin{document}

@@

\maketitle
% \thispagestyle{empty}

@@

By submitting a manuscript to 3DV, the authors assert that it has not been
previously published in substantially similar form. Furthermore, no paper
which contains significant overlap with the contributions of this paper
either has been or will be submitted during the 3DV 2016 review period to
{\bf either a journal} or any conference or any
workshop.  {\bf Papers violating this condition will be rejected}.

@@

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.  Just
because you didn't refer to it in the text doesn't mean some future reader
might not need to refer to it.  It is cumbersome to have to use
circumlocutions like ``the equation second from the top of page 3 column
1''.  (Note that the ruler will not be present in the final copy, so is not
an alternative to equation numbers).  All authors will benefit from reading
Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

@@

FAQ: Are acknowledgements OK?  No.  Leave them for the final copy.

@@

All printed material, including text, illustrations, and charts, must be
kept within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches
(22.54 cm) high.
